Clustering galaxy spectra at $0.5<z<1$: an unsupervised approach

### 2016-06-22 sections0.05/results0.05.tex
After Sophia and Aycha's comments.

    In this section we show the results of the neural networks trained using the K96 template spectra.
    Training with K96 templates results in networks that have regions corresponding to galaxies of known morphological type. 
    The trained networks can then be used to categorize other galaxies.
    %In following we show how we trained data and used galaxies from T12 to show how the clustering using trained networks works.

    In order to find a sufficient size for the trained networks, we created maps with sizes ranging from $1\times2$ to $50\times50$.
    Varying the grid size of the maps helps us to monitor whether tighter grouping of galaxies is due to their similar properties or a lack of map space to separate them.
   Based on the size of the data and SOM results, we found the optimum grid size to be $1\times22$ and $12\times12$ in 1D and 2D maps, respectively. 
    For each grid we created different SOMs with different learning factors, neighbourhood distances, and number of iterations to find the optimum.
    We create the final SOMs with initial values for number of iterations in ordering phase, ordering phase learning factor, tuning phase learning factor, and tuning phase neighbourhood distance of 1000, 0.9, 0.02, and 1, respectively.

    We started our analysis by creating 1D SOMs. 
    First, we created SOMs with only two neurons ($1\times2$ map), and then increased the number of neurons one at a time in the 1D case (Sec.~\ref{sec: 1D}).
    We generate 2D networks (Sec.~\ref{sec: 2D}),  again starting with the smallest possible number of neurons (4 neurons in a $2\times2$ map), increasing to 144 in a $12\times12$ map.    
    For each generated network, we compare the results with the K96 categorization.
    We also use these networks to classify the T12 galaxy sample, and compare this classification with that from the supervised networks in T12.

    \subsection{One-dimensional self-organizing maps}
    \label{sec: 1D}
        \subsubsection{TRAINING THE NETWORKS} %PB note: I've changed 'galaxy' to 'template' pretty much everywhere.
        \label{sec: 1Dt}
            To start our clustering, we assumed that galaxies can be divided into only two general types; quiescent and starburst.
            This corresponds to a network with only two neurons.
            We increased the size of the map gradually until the 12 input samples divide into the 12 neurons.

            Figs.~\ref{fig: 1by2T} --\ref{fig: 1by22T} show the results of the training networks.
            As in to Fig.~\ref{fig: sample}, the upper part of the figures shows the neurons and their relative distances, $D_j$.
            As mentioned in Sec.~\ref{sec: method}, an increase in the darkness of colours between neurons represents an increase in relative distance between the neurons.
            The lower panels of the figures show the number of K96 templates that are placed in each neuron. 
            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{images0.01/1d/dist_1_by_2.png}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{images0.01/1d/hit_t_1_by_2.png}
                \end{subfigure}
                \caption{Results of training network in $1\times2$~grid. As in Fig.~\ref{fig: sample}, the upper panel is a distance map and the lower panel is a hit map. In this network, 5 of the templates from K96 are categorized as quiescent galaxies and the rest are starbursts. Because of their strong emission lines, Sc galaxies are moved towards the starburst ones.}
                 \label{fig: 1by2T}
            \end{figure}

            In the upper map in Fig.~\ref{fig: 1by2T}, the dark colour between two neurons indicates that the relative distance between these two groups are relatively high, and these two groups are distinguishable groups.%(why do you keep reaping that?)
            In the lower part of Fig.~\ref{fig: 1by2T}, we see that the templates are divided into two groups of 5 and 7.
            Although we know from K96 and T12 that 6 of the templates are quiescent and the other 6 are starbursts, the SOM results show 5 of the galaxies in one group and the other 7 in the second group.
            In this method, the Sc template has been categorized as starburst due to the relatively higher disk stellar population relative to that of the bulge. 
            According to K96, Sc galaxies are considered to be late Hubble type galaxies which have a flattter SED compare to other quiescent galaxies.

            Fig.~\ref{fig: 1by3T} shows the results of the training in a 1$\times$3 network.
            In these plots we force the galaxies to be categorize in a maximum 3 groups. 
            %If the galaxies in Fig.~\ref{fig: 1by2T} were very similar to each other or were exactly the same, they still wanted to be divided into two groups and left the middle node empty(this sentence does not make much sense. I kind of think I know what you're trying to say (because once I translate this sentence to farsi word by word, it kind of comes together) but please phrase it more carefully.).
            %[suggested sentence: 
            If the templates in Fig.~\ref{fig: 1by2T} truly belonged in two groups, they would be grouped into two groups in this network, even when we try to cluster them into three. 
            However, in the lower panel of Fig.~\ref{fig: 1by3T}, we can see that the middle node contains two templates.
            These two templates, which are separated from the group of starburst templates in the lower part of Fig.~\ref{fig: 1by2T},  are the SB5 and SB6 types.
            In the upper plot of Fig.~\ref{fig: 1by3T}, the colour between two right neurons is black and the colour between two left neurons is white. 
            The black colour indicates that the left neuron is completely different from the other two groups,
            while the white colour shows that the two right neurons are very similar to one another.

@@

            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{images0.01/1d/dist_1_by_3.png}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{images0.01/1d/hit_t_1_by_3.png}
                \end{subfigure}
                \caption{The same as Fig.~\ref{fig: 1by2T} but showing the results of training network in $1\times3$~grid. In this network again, 5 of the K96 templates are categorized as quiescent and 7 as starbursts. However, this time 2  templates (SB5 and SB6) are separated from the starburst groups.}
                 \label{fig: 1by3T}
            \end{figure}

            We increased the size of the maps gradually until the galaxies are divided into twelve groups (Figs.~\ref{fig: 1by4T} to ~\ref{fig: 1by20T} and ~\ref{fig: 1by22T}).
            Since there are more nodes in higher grid SOMs, the  algorithm %program%(program? definitely use something else; like the algorithm?)  - algorithm is better - PB.
            pays more attention to small differences between groups.
 %           Increasing the size of maps means that even the smallest differences between galaxies have to be considered.
            If the templates from K96 had completely distinct SEDs, then a $1\times12$-sized SOM would be expected to show 12 different groups each containing a single template.
            However, in Fig.~\ref{fig: 1by12T}, we see that three of the neurons contain two templates and three of them are empty.
            It is evident that there was no template in the K96 sample that can fill those empty neurons.
            In Fig.~\ref{fig: 1by12T}, from left to right, templates with types B and E, SB3 and SB4, and SB1 and SB2 are the ones grouped together. 
            The SB3 and SB4 grouping breaks when we increase the size of the network to $1\times15$~(Fig.~\ref{fig: 1by15T}).
            The SB1 and SB2 templates, however, remain in the same neuron until the size of the map is increased to $1\times20$~(Fig.~\ref{fig: 1by20T}).
            The separation between templates B and E only happens when the size of the SOM exceeds $1\times22$~(Fig.~\ref{fig: 1by22T}).
        \begin{figure*}
            \begin{subfigure}[b]{\textwidth}
                \centering
                \includegraphics[width=\textwidth]{images0.01/1d/dist_1_by_22.png}
            %\caption{$1\times22$ weight map}
             %\label{fig: 1by22T}
            \end{subfigure}
            \hfill
            \begin{subfigure}[b]{\textwidth}
                \includegraphics[width=\textwidth]{images0.01/1d/hit_t_1_by_22.png}
             %\caption{$1\times22$ hits map}
             %\label{fig: 1by22Thits}
            \end{subfigure}
            \caption{The same as Fig.~\ref{fig: 1by2T} but this time the figure shows results of training network in $1\times22$~grid.}
            \label{fig: 1by22T}
        \end{figure*} %PB160427: this figure looks really great! Very easy to understand.

@@

        \subsubsection{Classifying the galaxy sample}
         \label{sec: 1Dv}
            After training the networks as discussed in Sec.~\ref{sec: 1Dt}, we used them to classify the fitted SEDs of the sample of 142 galaxies from T12.
            The upper panel in Fig.~\ref{fig: 1by2V} shows the result of this classification using the $1\times2$~network from Fig.~\ref{fig: 1by2T}.
            Eighty of the galaxies have SEDs similar to those of the early type galaxies and the SEDs of the rest are similar to the starburst galaxies.
            %The lower panels show the average SED of the galaxies in each node. 
            The lower left panel shows the average SED of the 80 galaxies that were classified as early type 
            These galaxies are similar to the ones in the left node in the upper panel of Fig.~\ref{fig: 1by2T}:
            the SEDs clearly show the 4000\AA~break, one of the signatures of early type galaxies.
            The H$\alpha$ emission in the spectrum could be from galaxies with similar SEDs to Sa galaxies, but with stronger emission lines.
            The average SED in the lower right panel of Fig.~\ref{fig: 1by2V} shows strong emission lines and bright ultraviolet continuum, indications of a high star formation rate.
            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{images0.01/1d/hit_v_1_by_2.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{images0.01/1d/SED_total1by2.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Classification of fitted galaxy SEDs from T12 using the $1\times2$~networks trained from the K96 templates (Fig.~\ref{fig: 1by2T}). Upper panel: a hit map with the number in each node representing the number of galaxies belonging to that group. In this case 80 means that 80 of the 142 SEDs are classified into the early type group while the 62 of the 142 SEDs are categorized as starburst galaxies. Lower panel: Average SED of the galaxies in each group, early-type on the left and starburst on the right.}
                \label{fig: 1by2V}
            \end{figure}

@@

            In Fig.~\ref{fig: 1by22V}, we use the $1\times22$~network to classify the sample galaxies.
            As mentioned in Sec.~\ref{sec: 1Dt}, in this network size we observed the first separation of the K96 galaxies into 12 different neurons.
           As in Figs.~\ref{fig: 1by2V} and ~\ref{fig: 1by3V}, the upper panel of Fig.~\ref{fig: 1by22V} shows the number of galaxies (out of the 142) belonging to each neuron in the $1\times22$ SOM.
            \begin{figure*}
                \begin{subfigure}[b]{0.9\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{images0.01/1d/hit_v_1_by_22_n.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.9\textwidth}
                     \includegraphics[width=\textwidth]{images0.01/1d/SED_total1by22.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Same as Fig.~\ref{fig: 1by2V}, but in this figure, we used a network with size of $1\times22$ (Fig.~\ref{fig: 1by22T}) to classify the sample galaxies. In the average SED of each neuron, we can clearly see the changes from early type galaxies to the starburst ones. The 4000\AA~ break weakens from left to right and the emission line strengths increase.}
                \label{fig: 1by22V}
            \end{figure*}
            The lower panels present the average SED of the galaxies in each neuron.
            Since galaxies had more space to separate, some of the neurons are left empty.
            Thus, instead of having 22 average SED plots in the lower part of Fig.~\ref{fig: 1by22V}, there are only 12.

            Comparing the upper panel of Fig.~\ref{fig: 1by22V} with the lower panel of Fig.~\ref{fig: 1by22T} shows that the occupied neurons are not necessarily the same.
            If a cluster from the T12 sample fills the same neuron as a K96 template, we can conclude that SEDs of galaxies in the cluster are very similar to those of the template.
            Otherwise, we can conclude that the SEDs of galaxies in the cluster are similar to two of the K96 templates.
            For the latter case, the colours establish which template has greater similarity to the T12 cluster.

            The first two neurons in the upper plot in Fig.~\ref{fig: 1by22V} are empty, while these neurons were occupied by galaxies B and E in the trained network.
            We therefore conclude that there are no galaxies in the T12 sample with SEDs similar to that of type B or E.
            There are 3 galaxies in the third neuron, similar to the S0 type. 
            18 of the galaxies are jn the fifth neurons and similar to the Sa type, while the 7 galaxies in the fourth neurons have SEDs similar to both S0 and Sa galaxies.
            There is one Sb type galaxy and 15 galaxies with SEDs similar to both Sa and Sb type galaxies.
            The following two neurons (eighth and ninth neurons from the left) are on the edge of the early type and starburst galaxies.
            In the upper panel in Fig.~\ref{fig: 1by22T}, the colour between these two neurons is black, which shows that these two are very different.
            Therefore, 24 galaxies in the eighth neurons have similar SEDs to Sb type galaxies, and the SEDs of the 14 galaxies in the ninth neuron are similar to the SB6 galaxies.
            The far right neurons in the network belong to galaxies with SED comparable to types SB1 and SB2.

            In general, 56 galaxies correspond exactly to K96 templates and the other 86 are placed between the initial 12 suggestions.
            As T12 mentioned, part of the reason we could not classify all the galaxies using the K96 model is that the model was constructed from co-adding spectra of 70 galaxies.
            In this small sample, it is quite possible that the best SEDs do not match any model perfectly and the original classifications have high uncertainties.

            %PB20160604: is this paragraph really necessary?
            With other methods (e.g. $\chi^2$ fitting), trained neural network fitting of SEDs is limited to models and the results are always reported with uncertainties.
            However, with SOM, we have the freedom to categorize galaxies in intermediate groups.
            Therefore, if the SED of galaxies do not match completely with any of the model SEDs in Fig.~\ref{fig: k96}, they can be categorized as a SED with similarity to two or more of the groups.

@@

        In order to check whether our conclusions in Sec.~\ref{sec: 1Dv}~are correct, in this section we test the relations between median properties of the galaxies in each neuron.

@@

%PB20160604: this paragraph needs a topic sentence.
        N09 used various models to derive the properties of galaxies.
        Through these models, some of the properties are already known to be correlated with each other, e.g., stellar mass and star formation rate.
        They also studied other relations between properties with no direct correlation in the models in a sample of SINGS galaxies. %%eHMM I will change the previous sentence! It doesn't read well
        They found a tight correlation between sSFR and t$_{\rm {D4000}}$, which suggests that younger stellar population correlates with higher SFR.
        They also found correlations between stellar mass and SFR, and stellar mass and t$_{\rm {D4000}}$.
        Since in the {\sc CIGALE} code, stellar mass is a free parameter, N09 argued that any stellar-mass-related correlation must be astrophysically meaningful. 
        They also studied relations between the attenuation at 1500 \AA~(A$_{\rm {FUV}}$) and sSFR, age, and stellar mass and did not find any correlation.
        T12 replicated the upper plots in Fig.~\ref{fig: props_vs_props}, and found a tighter correlation than N09 results.

               \begin{figure*}
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{images0.01/1d/f1.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{images0.01/1d/f2.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{images0.01/1d/f3.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{images0.01/1d/f4.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{images0.01/1d/f5.png}
        \end{subfigure}
       \hfill
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{images0.01/1d/f6.png}
        \end{subfigure}
        \caption{From top to bottom: Correlation between age (t$_{\rm {D4000}}$) and sSFR ($\phi$), sSFR and stellar mass, age (t$_{\rm {D4000}}$) and stellar mass, and A$_{\rm {FUV}}$ with sSFR, age (t$_{\rm {D4000}}$) and stellar mass. Points show the mean values of these properties of galaxies in $1\times22$ network and error bars are the standard deviation of the mean values. colours shows the type of the galaxies in the new classification. The most pure red colour shows E type galaxies and the most blue one indicates the SB1 galaxies. The other colours depend on how much they are close to red or blue show that the galaxies are early type or starburst.}
        \label{fig: props_vs_props}
    \end{figure*}

>>>>

    In this section we show the results of the neural networks trained using the 12 \citetalias{Kinney96} template spectra.
    Training with \citetalias{Kinney96} templates results in networks that have regions corresponding to galaxies of known morphological type. 
    The trained networks can then be used to categorize other galaxies.

    In order to find a sufficient size for the trained networks, we created maps with sizes ranging from $1\times2$ to $50\times50$.
    Varying the grid size of the maps helps us to monitor whether tighter grouping of galaxies is due to their similar properties or a lack of map space to separate them.
    Based on the size of the data and SOM results, we found the optimum grid size to be $1\times22$ and $12\times12$ in 1D and 2D maps, respectively. 
    For each grid we created different SOMs with different learning factors, neighbourhood distances, and number of iterations to find the most suitable values for our dataset, which are listed in Section~\ref{sec: create_som}. %%%Sr220616: changed the optimum to the most suitable values ... . moved the initial values to section 3.2

    We started our analysis by creating 1D SOMs. 
    First, we created SOMs with only two neurons ($1\times2$ map), and then increased the number of neurons one at a time in the 1D case (Sec.~\ref{sec: 1D}).
    We generate 2D networks (Sec.~\ref{sec: 2D}),  again starting with the smallest possible number of neurons (4 neurons in a $2\times2$ map), increasing to 144 in a $12\times12$ map.    
    For each generated network, we compare the results with the \citetalias{Kinney96} categorization.
    We also use these networks to classify the \citetalias{Hossein12} galaxy sample, and compare this classification with that from the supervised networks in \citetalias{Hossein12}.

    \subsection{One-dimensional self-organizing maps}
    \label{sec: 1D}
        \subsubsection{TRAINING THE NETWORKS}
        \label{sec: 1Dt}
            To start our clustering, we assumed that galaxies can be divided into only two general types; quiescent and starburst.
            This corresponds to a network with only two neurons.
            We increased the size of the map gradually until the 12 input samples divide into the 12 neurons.

            Figs.~\ref{fig: 1by2T} --\ref{fig: 1by22T}~show the results of the training $1\times2$, $1\times3$, and $1\times22$ networks, respectively (The rest of the networks are shown in Appendix~\ref{app: high_Z_1d_soms}.
            As in to Fig.~\ref{fig: sample}, the upper part of the figures shows the neurons and their relative distances, $D_j$.
            As mentioned in Sec.~\ref{sec: method}, an increase in the darkness of colours between neurons represents an increase in relative distance between the neurons.
            The lower panels of the figures show the number of \citetalias{Kinney96} templates that are placed in each neuron. 
            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{images0.01/1d/dist_1_by_2.png}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{images0.01/1d/hit_t_1_by_2.png}
                \end{subfigure}
                \caption{Results of training network in $1\times2$~grid. As in Fig.~\ref{fig: sample}, the upper panel is a distance map and the lower panel is a hit map. In this network, 5 of the templates from \citetalias{Kinney96} are categorized as quiescent galaxies and the rest are starbursts. Because of their strong emission lines, Sc galaxies are moved towards the starburst ones.}
                 \label{fig: 1by2T}
            \end{figure}

            In the upper map in Fig.~\ref{fig: 1by2T}, the dark colour between two neurons indicates that the relative distance between these two groups are relatively high, and these two groups are distinguishable groups.
            In the lower part of Fig.~\ref{fig: 1by2T}, we see that the templates are divided into two groups of 5 and 7.
            Although we know from \citetalias{Kinney96} and \citetalias{Hossein12} that 6 of the templates are quiescent and the other 6 are starbursts, the SOM results show 5 of the galaxies in one group and the other 7 in the second group.
            In this method, the Sc template has been categorized as starburst due to the relatively higher disk stellar population relative to that of the bulge. 
            According to \citetalias{Kinney96}, Sc galaxies are considered to be late Hubble type galaxies which have a flattter SED compare to other quiescent galaxies.

            Fig.~\ref{fig: 1by3T} shows the results of the training in a 1$\times$3 network.
            In these plots we force the galaxies to be categorize in a maximum 3 groups. 
            If the templates in Fig.~\ref{fig: 1by2T} truly belonged in two groups, they would be grouped into two groups in this network, even when we try to cluster them into three. 
            However, in the lower panel of Fig.~\ref{fig: 1by3T}, we can see that the middle node contains two templates.
            These two templates, which are separated from the group of starburst templates in the lower part of Fig.~\ref{fig: 1by2T},  are the SB5 and SB6 types.
            In the upper plot of Fig.~\ref{fig: 1by3T}, the colour between two right neurons is black and the colour between two left neurons is white. 
            The black colour indicates that the left neuron is completely different from the other two groups,
            while the white colour shows that the two right neurons are very similar to one another.

@@

            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{images0.01/1d/dist_1_by_3.png}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{images0.01/1d/hit_t_1_by_3.png}
                \end{subfigure}
                \caption{The same as Fig.~\ref{fig: 1by2T} but showing the results of training network in $1\times3$~grid. In this network again, 5 of the \citetalias{Kinney96} templates are categorized as quiescent and 7 as starbursts. However, this time 2  templates (SB5 and SB6) are separated from the starburst groups.}
                 \label{fig: 1by3T}
            \end{figure}

            We increased the size of the maps gradually until the galaxies are divided into twelve groups (Figs.~\ref{fig: 1by4T} to ~\ref{fig: 1by20T} and ~\ref{fig: 1by22T}).
            Since there are more nodes in higher grid SOMs, the  algorithm 
            pays more attention to small differences between groups.
            If the templates from \citetalias{Kinney96} had completely distinct SEDs, then a $1\times12$-sized SOM would be expected to show 12 different groups each containing a single template.
            However, in Fig.~\ref{fig: 1by12T}, we see that three of the neurons contain two templates and three of them are empty.
            It is evident that there was no template in the \citetalias{Kinney96} sample that can fill those empty neurons.
            In Fig.~\ref{fig: 1by12T}, from left to right, templates with types B and E, SB3 and SB4, and SB1 and SB2 are the ones grouped together. 
            The SB3 and SB4 grouping breaks when we increase the size of the network to $1\times15$~(Fig.~\ref{fig: 1by15T}).
            The SB1 and SB2 templates, however, remain in the same neuron until the size of the map is increased to $1\times20$~(Fig.~\ref{fig: 1by20T}).
            The separation between templates B and E only happens when the size of the SOM exceeds $1\times22$~(Fig.~\ref{fig: 1by22T}).
        \begin{figure*}
            \begin{subfigure}[b]{\textwidth}
                \centering
                \includegraphics[width=\textwidth]{images0.01/1d/dist_1_by_22.png}
            %\caption{$1\times22$ weight map}
             %\label{fig: 1by22T}
            \end{subfigure}
            \hfill
            \begin{subfigure}[b]{\textwidth}
                \includegraphics[width=\textwidth]{images0.01/1d/hit_t_1_by_22.png}
             %\caption{$1\times22$ hits map}
             %\label{fig: 1by22Thits}
            \end{subfigure}
            \caption{The same as Fig.~\ref{fig: 1by2T} but this time the figure shows results of training network in $1\times22$~grid.}
            \label{fig: 1by22T}
        \end{figure*} %PB160427: this figure looks really great! Very easy to understand.

@@

        \subsubsection{Classifying the galaxy sample}
         \label{sec: 1Dv}
            After training the networks as discussed in Sec.~\ref{sec: 1Dt}, we used them to classify the fitted SEDs of the sample of 142 galaxies from \citetalias{Hossein12}.
            The upper panel in Fig.~\ref{fig: 1by2V} shows the result of this classification using the $1\times2$~network from Fig.~\ref{fig: 1by2T}.
            Eighty of the galaxies have SEDs similar to those of the early type galaxies and the SEDs of the rest are similar to the starburst galaxies.
            %The lower panels show the average SED of the galaxies in each node. 
            The lower left panel shows the average SED of the 80 galaxies that were classified as early type 
            These galaxies are similar to the ones in the left node in the upper panel of Fig.~\ref{fig: 1by2T}:
            the SEDs clearly show the 4000\AA~break, one of the signatures of early type galaxies.
            The H$\alpha$ emission in the spectrum could be from galaxies with similar SEDs to Sa galaxies, but with stronger emission lines.
            The average SED in the lower right panel of Fig.~\ref{fig: 1by2V} shows strong emission lines and bright ultraviolet continuum, indications of a high star formation rate.
            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{images0.01/1d/hit_v_1_by_2.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{images0.01/1d/SED_total1by2.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Classification of fitted galaxy SEDs from \citetalias{Hossein12} using the $1\times2$~networks trained from the \citetalias{Kinney96} templates (Fig.~\ref{fig: 1by2T}). Upper panel: a hit map with the number in each node representing the number of galaxies belonging to that group. In this case 80 means that 80 of the 142 SEDs are classified into the early type group while the 62 of the 142 SEDs are categorized as starburst galaxies. Lower panel: Average SED of the galaxies in each group, early-type on the left and starburst on the right.}
                \label{fig: 1by2V}
            \end{figure}

@@

            In Fig.~\ref{fig: 1by22V}, we use the $1\times22$~network to classify the sample galaxies.
            As mentioned in Sec.~\ref{sec: 1Dt}, in this network size we observed the first separation of the \citetalias{Kinney96} galaxies into 12 different neurons.
           As in Figs.~\ref{fig: 1by2V} and ~\ref{fig: 1by3V}, the upper panel of Fig.~\ref{fig: 1by22V} shows the number of galaxies (out of the 142) belonging to each neuron in the $1\times22$ SOM.
            \begin{figure*}
                \begin{subfigure}[b]{0.9\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{images0.01/1d/hit_v_1_by_22_n.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.9\textwidth}
                     \includegraphics[width=\textwidth]{images0.01/1d/SED_total1by22.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Same as Fig.~\ref{fig: 1by2V}, but in this figure, we used a network with size of $1\times22$ (Fig.~\ref{fig: 1by22T}) to classify the sample galaxies. In the average SED of each neuron, we can clearly see the changes from early type galaxies to the starburst ones. The 4000\AA~ break weakens from left to right and the emission line strengths increase.}
                \label{fig: 1by22V}
            \end{figure*}
            The lower panels present the average SED of the galaxies in each neuron.
            Since galaxies had more space to separate, some of the neurons are left empty.
            Thus, instead of having 22 average SED plots in the lower part of Fig.~\ref{fig: 1by22V}, there are only 12.

            Comparing the upper panel of Fig.~\ref{fig: 1by22V} with the lower panel of Fig.~\ref{fig: 1by22T} shows that the occupied neurons are not necessarily the same.
            If a cluster from the \citetalias{Hossein12} sample fills the same neuron as a \citetalias{Kinney96} template, we can conclude that SEDs of galaxies in the cluster are very similar to those of the template.
            Otherwise, we can conclude that the SEDs of galaxies in the cluster are similar to two of the \citetalias{Kinney96} templates.
            For the latter case, the colours establish which template has greater similarity to the \citetalias{Hossein12} cluster.

            The first two neurons in the upper plot in Fig.~\ref{fig: 1by22V} are empty, while these neurons were occupied by galaxies B and E in the trained network.
            We therefore conclude that there are no galaxies in the \citetalias{Hossein12} sample with SEDs similar to that of type B or E.
            There are 3 galaxies in the third neuron, similar to the S0 type. 
            18 of the galaxies are jn the fifth neurons and similar to the Sa type, while the 7 galaxies in the fourth neurons have SEDs similar to both S0 and Sa galaxies.
            There is one Sb type galaxy and 15 galaxies with SEDs similar to both Sa and Sb type galaxies.
            The following two neurons (eighth and ninth neurons from the left) are on the edge of the early type and starburst galaxies.
            In the upper panel in Fig.~\ref{fig: 1by22T}, the colour between these two neurons is black, which shows that these two are very different.
            Therefore, 24 galaxies in the eighth neurons have similar SEDs to Sb type galaxies, and the SEDs of the 14 galaxies in the ninth neuron are similar to the SB6 galaxies.
            The far right neurons in the network belong to galaxies with SED comparable to types SB1 and SB2.

            In general, 56 galaxies correspond exactly to \citetalias{Kinney96} templates and the other 86 are placed between the initial 12 suggestions.
            As \citetalias{Hossein12} mentioned, part of the reason we could not classify all the galaxies using the \citetalias{Kinney96} model is that the model was constructed from co-adding spectra of 70 galaxies.
            In this small sample, it is quite possible that the best SEDs do not match any model perfectly and the original classifications have high uncertainties.

            %PB20160604: is this paragraph really necessary?
            %%Sr: I think it clears the point of having regions in middle neurons
            %%%%%%%Sr220616: I almost completely changed the following paragraph, but I think it makes more sense, now.
            Other methods for finding the type of galaxies (e.g. $\chi^2$ fitting and supervised neural network) are limited to templates and the outliers are not classified.
            However, using SOM method we categorized galaxies based on their position on trained SOMs, which can have empty neurons.
            The empty neurons in a trained SOM show that there must be another type of template there, that is absent from the K96 template spectra.
            Using the distance of the trained network is the best way to describe the properties of this absent template.
            Therefore, with SOM, we have the freedom to categorize galaxies in intermediate (new) templates.
            %%%%%%%Sr220616: in response to Sophia's comment; In SOM we do not fit the data. we create a network using our template. In the final version of network each neuron has a weight vector. When we give a new data to this weight vector, based on distance of the the weight vector and a new input data, the SOM finds a winner neuron. If this winner neurons were the same for K96 and T12 samples, we would say the input vector in these two case were similar. Since we know type of the galaxies in K96, we could decide about the type of the galaxies in T12.

@@

        In order to check whether our clustering in Sec.~\ref{sec: 1Dv}~are correct, in this section we test the relations between median properties of the galaxies in each neuron.  %%%%%%%Sr220616:changed "conclusion" to clustering!

@@

        %Sr07062016: Is it better?
        {\sc CIGALE} has various models to derive the properties of galaxies.
        Through these models, some of the properties are already known to be correlated with each other, e.g., stellar mass and star formation rate.
        \citetalias{Noll09} studied other relations between properties with no direct correlation in the models in a sample of SINGS galaxies.
        They found a tight correlation between sSFR and t$_{\rm {D4000}}$, which suggests that younger stellar population correlates with higher SFR.
        They also found correlations between stellar mass and SFR, and stellar mass and t$_{\rm {D4000}}$.
        Since in the {\sc CIGALE} code, stellar mass is a free parameter, \citetalias{Noll09} argued that any stellar-mass-related correlation must be astrophysically meaningful. 
        They also studied relations between the attenuation at 1500 \AA~(A$_{\rm {FUV}}$) and sSFR, age, and stellar mass and did not find any correlation.
        \citetalias{Hossein12} replicated the upper plots in Fig.~\ref{fig: props_vs_props}, and found a tighter correlation than \citetalias{Noll09} results.

               \begin{figure*}
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{images0.01/1d/f1.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{images0.01/1d/f2.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{images0.01/1d/f3.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{images0.01/1d/f4.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{images0.01/1d/f5.png}
        \end{subfigure}
       \hfill
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{images0.01/1d/f6.png}
        \end{subfigure}
        \caption{From top to bottom: Correlation between age (t$_{\rm {D4000}}$) and sSFR ($\phi$), sSFR and stellar mass, age (t$_{\rm {D4000}}$) and stellar mass, and A$_{\rm {FUV}}$ with sSFR, age (t$_{\rm {D4000}}$) and stellar mass. Points show the median values of these properties of galaxies in $1\times22$ network and error bars are the standard deviation of the median values. colours shows the type of the galaxies in the new classification. The most pure red colour shows E type galaxies and the most blue one indicates the SB1 galaxies. The other colours depend on how much they are close to red or blue show that the galaxies are early type or starburst.}
        \label{fig: props_vs_props}
    \end{figure*}

        In order to compare our classifications with previous works, we produced similar plots to the ones in both \citetalias{Noll09} and \citetalias{Hossein12} (Fig.~\ref{fig: props_vs_props}).
        In Fig.~\ref{fig: props_vs_props}, the data points are median values of the properties of the galaxies in each neuron in Fig.~\ref{fig: 1by22V}, and error bars show the standard deviation of those properties.
        The colours show the galaxy types, where B type galaxies are shown with red and SB1 types are shown with blue.
        The redder the colour, the more similarity with early type galaxies, while the purple to blue colours show more similarity to starburst galaxies.
        Since in this method we allow galaxies to occupy classes in between the original \citetalias{Kinney96} templates, we have more than 12 colours in Fig.~\ref{fig: props_vs_props}.
        The purple point in the middle of the blue points in  Fig.~\ref{fig: props_vs_props} corresponds to galaxies with SEDs similar to type Sc: the shape of their SED indicates that they are old galaxies with high sSFR.

        The upper panels in Fig.~\ref{fig: props_vs_props} show the same relations as \citetalias{Noll09} and \citetalias{Hossein12}, but with tighter correlation than those two, in all three plots.
        As mentioned in both \citetalias{Noll09} and \citetalias{Hossein12}, galaxies with smaller mass tend to be younger and more active.
        Fig.~\ref{fig: props} shows similar results: younger and more active galaxies have less stellar mass and more f$_{\rm {burst}}$.
        From older to younger galaxies, the colour of the points changes from red to blue, which shows a good correlation with their SED type.
        %for more details discussion on these correlations, we encourage readers to read \citetalias{Noll09} and \citetalias{Hossein12}.
